\documentclass[letterpaper,12pt]{article}
\usepackage[top=2.5cm, left=2.5cm, right=2.5cm, foot=1.5cm, bottom=2.5cm]{geometry}
\usepackage{latexsym}
\usepackage{verbatim}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=black, filecolor=black, linkcolor=blue, urlcolor=blue}


\definecolor{mygrey}{gray}{.90}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins

%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{0.375in}
%\addtolength{\textwidth}{0.5in}
%\addtolength{\topmargin}{-.375in}
%\addtolength{\bottommargin}{-.375in}
%\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheadingnew}[6]{
\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} \\
		\textit{#6}
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\projectitem}[2]{
\begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} 
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}
\newcommand{\myheader}{
\begin{tabular*}{6.4in}{l@{\extracolsep{\fill}}r}
	\textbf{\LARGE Sudha Rao}\\
	 & 609-933-0409\\
	 & raosudha@cs.umd.edu\\
	\end{tabular*}
\\
\vspace{0.1in}}

\myheader
\hrule
~\\
~\\
\resheading{Education}
\begin{itemize}
\item []\ressubheadingnew{University of Maryland, College Park}{}{PhD - Computer Science}{2013 - 2018 (expected)} {Focus: Natural Language Processing}{Advisors: Hal Daum\'e III, Philip Resnik}
\item []\ressubheading{Veermata Jijabai Technological Institute}{Mumbai}{Bachelor of Technology - Computer Engineering; CPI:9.4/10}{May 2011}
\end{itemize}

\resheading{Publications}
{\footnotesize
\begin{itemize}
\item \textbf{Sudha Rao}, Yogarshi Vyas, Hal Daum\'e III, and Philip Resnik.  \textbf{Parser for Abstract Meaning Representation using Learning to Search} \textit{Under submission}
\item \textbf{Sudha Rao}, Allyson Ettinger, Hal Daum\'e III, and Philip Resnik, \textbf{Dialogue focus tracking for zero pronoun resolution}, NAACL 2015, Denver, Colorado, June 2015.
\item 
Suzanne D’Silva, Neha Joshi, \textbf{Sudha Rao}, Sangeetha Venkatraman, and Seema Shrawne.  {\textbf{Improved Algorithms for Document Classification \& Query-based Multi-Document Summarization}}, \textit{International Journal of Engineering and Technology vol. 3, no. 4, pp. 404-409 , 2011}
\end{itemize}
}

\resheading{Research Experience}
\begin{itemize}
\item
\projectitem {Semantics for biology}{Summer 2015}
{\footnotesize
  \begin{itemize}
  \item Working on identifying protein interactions in biology texts using \textbf{Abstract Meaning Representation (AMR)} of sentences.
  \item This work is a part of the \textbf {\textit{Big Mechanism}} project and I am working on this with \textbf{Dr. Daniel Marcu} and \textbf{Dr. Kevin Knight} at \textbf{ISI, USC}.
  \end{itemize}
}
\item
\projectitem {Semantic Parsing}{Fall 2014}
{\footnotesize
  \begin{itemize}
  \item Worked on automatically learning \textbf{Abstract Meaning Representation (AMR)} for English sentences using \textbf{SEARN} $($Search based Structured Prediction$)$ technique.
  \end{itemize}
}
\item
\projectitem {Machine Translation}{Spring 2013}
{\footnotesize
  \begin{itemize}
  \item Worked on developing a \textbf{Sequence Labeling} model for restoring \textbf{dropped pronouns} when translating SMS text from Chinese to English.
  \item This work was done as a part of \textbf{IBM's BOLT} project.
  \end{itemize}
}

\item 
\projectitem  {Query based Multi-document Summarization}{Spring 2011}
{\footnotesize
  \begin{itemize}
  \item Analyzed and \textbf{improved a Hypergraph based technique} for summarization to make it less processor intensive.
  \item Designed a simple algorithm for query based multi-document summarization using \textbf{k-means clustering} with results comparable to the Hypergraph based technique.
  \end{itemize}
}
\end{itemize}

\resheading{Work Experience}
\begin {itemize}
 \item
\ressubheading{NVIDIA Graphics Pvt. Ltd.}{Pune}{System Software Engineer}{July 2011 -- April 2013}
{\footnotesize
  \begin{itemize}
  \item Designed and implemented a test infrastructure for Tegra Driver on varied mobile operating systems and platforms.
  \item Worked on in-house mobile tools being developed as a part of \textit{Planning, Infrastructure \& Operations} team.
  \end{itemize}
}
\item
\ressubheading{Microsoft India Development Center}{Hyderabad}{Software Development Engineer - Intern}{May 2010 -- July 2010}
{\footnotesize
  \begin{itemize}
  \item Worked on Data Protection Management.
  \end{itemize}
}
\end{itemize}

\resheading{Teaching Experience}
\begin{itemize}
\item []
 \ressubheading {CMSC 131 - Object Oriented Programming} {Fall 2013} {}{}
 \end{itemize}

\resheading{Projects}
\begin{itemize}
\item
\projectitem{Predicting clinical depression}{Spring 2013}
{\footnotesize
  \begin{itemize}
\item We used \textbf{Facebook status updates} to predict neuroticism among people.
\item This project was done as a part of the \textbf{Computational Linguistics} course.
  \end{itemize}
}
\item
\projectitem{Farmer’s Buddy}{Fall 2009}
{\footnotesize
  \begin{itemize}
  \item We developed a first of its kind portal to be accessible via Internet allowing users, especially farmers, to obtain information regarding various activities involved in farming and providing a platform for interaction between the different users of the system.
  \item This project was developed as part of \textbf{IBM's The Great Mind Challenge}, 2009, and was among the \textbf{Top 20} projects all over India.
  \end{itemize}
}
\end{itemize}


\resheading{Honours/Awards}
{\footnotesize
\begin{itemize}
\item Scholarship to attend the \textbf{Grace Hopper Celebration} conference 2014.
\item Recipient of \textbf{Dean's Fellowship} at University of Maryland, College Park.
\item Travel fund to attend \textbf{NIPS} conference 2013.
\item Scholarship to attend the \textbf{Women in Theory} conference 2012 at Princeton University.
\item Ranked \textbf{3rd} out of 70 students in the Computer Science department of VJTI.
\item Recipient of scholarship award from \textbf{Sir Ratan Tata} Trust (2008, 2009 and 2010).
\item \textbf{56th} rank in Maharashtra in MHT-CET examination held in May – 2007 in Engineering Course. Score: \textbf{(194 / 200)}
\end{itemize}

\resheading{Technical Skills}
{\footnotesize
\begin{itemize}
\item \textbf{Languages:} Python, Java, C++, C\#, SQL, Perl
\item \textbf{Web Technologies:} J2EE(JSP, Servlet), HTML, CSS, Javascript, AJAX
\item \textbf{Databases:} Microsoft SQL, IBM DB2
\item \textbf{Operating Systems:} Linux, OS X, Microsoft Windows
\end{itemize}
}
\end{document}
